### 2020-05-14 Report/aws_325ghz_study.tex
updated correction section

\section{Cloud correction by a simple scheme}
%

\begin{figure}[!tb]
	\centering
	\includegraphics[height=65mm]{fit_C34_C42}\hspace{5mm}% 
	\caption{Brightness temperature difference of channel-34 from channel-42 plotted against cloud impact in channel-34 (TB allsky - TB cleasky). The black curve represents the line of best fit as a third order polynomial. }
	\label{fig:fit:c34-42}
\end{figure}

\begin{figure}[!th]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_C34_C42}
	\caption{Deviation of channel-34 measurements to noise free clear-sky cases. The various curves represent the measurements before and after correction. The correction according to \cite{rekha2012potential} is also shown. The two curves with label ``after correction'' are for two different values of noise threshold. }
	\label{fig:correction:c34-42}
\end{figure}

In this section, the 325GHz three channel option  is evaluated for ice cloud correction for 183 GHz channels. We predict the clears-sky value for 183GHz channel based on the brightness temperatures of simulated 325GHz channel data. For correction, the channels from the three option 325GHz and 183GHz are matched according to their weighting functions(Figure~\ref{fig:3ch:prel}). From the five  183 GHz and 325 GHz combinations possible, the weighting functions for channel- 34 and channel-42 have the best match, thus we use this combination for the development of the correction scheme.

A simple regression approach is implemented to estimate the clear-sky values from the measurements. From the simulation dataset, 40000 clear-sky and the corresponding all-sky simulations are selected to develop the correction scheme. Without the availability of actual data, an identical simulation dataset but with noise is used mimic the measurements. The noise for individual channels is calculated according to Equation~\ref{eq:noise}. Before deriving any relationship between the different variables, 50\% of the clear-sky simulations are removed from the dataset. This clear-sky removal is to remove any under-representation of cloudy simulations, as discussed in the Validation section. Further, the simulations from channel-34 with cloud impact greater than 25 K are considered as "too cloudy" and are not included in the correction.

Among the various possible combinations of clear-sky and all-sky pairs for channel-34 and channel-43, the brightness temperature (TB)  differences of channels-34 and 42 are found to be reasonably well correlated against the channel-34 cloud impact (TB clear-sky minus all-sky ). Figure ~\ref{fig:fit:c34-42}  shows the scatter plot of the TB channel-34 minus TB channel-42 against the channel-34 cloud impact. The regression between the two variables gives the correction estimate for channel-34 all-sky measurements :
\begin{equation}
correction = tb^{34} + f(tb0^{42}_{as} - tb0^{32}_{cs})   
\end{equation}
where, $ tb^{34}$ are channel-34 measurements, and $tb0^{42}_{as}$ and $tb0^{32}_{cs}$ are channel-42 and channel-34 simulations for all-sky and clear-sky respectively. 
The correction is applied only to cloudy measurements. All cases with cloud impact less than 0.2 K or greater than 25 K are termed as ``clear'' or ``too cloudy''  respectively and are not corrected. Further, all measurements with TB differences between channel-34 and channel-42 greater than a ``noise-index'' are not adjusted. This check is introduced to avoid correction of clear-sky measurements which are falsely classified as cloudy. the ``noise-index'' is defined as a factor the standard deviation of noise for 183GHz.

The error in the predicted measurements is assessed by calculating the deviation to noise-free clear-sky observations. The occurrence frequency of the deviations is shown in Figure~\ref{fig:correction:c34-42}. When all measurements are corrected for cloud impact, the deviations should follow a gaussian distribution with zero mean. However, without any correction, the measurements show a strong cloud impact, which is indicated by the non-zero values to the left of the peak (orange line). Removing measurements with cloud impact greater than 25 K (green line) reduces the cloud impact far left but not in the intermediate region indicating that it effectively removes the ``too cloudy'' measurements. After adjustment, the cloudy impact in the measurements is considerably reduced, though the spread increases. The sensitivity of the algorithm to correctly adjust the cloudy cases is tested through two different values of the noise-index: $1 \sigma$ and $2\sigma$. As evident from the figure, both values gave almost similar results indicating that the algorithm can correctly identify and adjust most of the cloudy measurements.

>>>>

\section{Cloud correction by a simple scheme}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=65mm]{fit_C34_C42}\hspace{5mm}% 
	\caption{Brightness temperature difference of channel-34 from channel-42 plotted against cloud impact in channel-34 (TB allsky - TB cleasky). The black curve represents the line of best fit as a third order polynomial. }
	\label{fig:fit:c34-42}
\end{figure}

\begin{figure}[!th]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_C34_C42}
	\caption{Deviation of channel-34 measurements to noise free clear-sky simulations. The various curves represent the measurements before and after correction. The correction according to \cite{rekha2012potential} is also shown. The two curves with label ``after correction'' are for two different values of clear-sky threshold. The fraction of cases rejected by the regression approach are given as ``fraction rejected'' in the title, while the number in the parentheses is fraction of cases rejected according  to \cite{rekha2012potential}. The average deviation for each dataset is also provided in the legend. }
	\label{fig:correction:c34-42}
\end{figure}

In this section, the 325GHz three channel option  is evaluated for ice cloud correction for 183 GHz channels. We predict the clears-sky value for 183GHz channel based on the brightness temperatures of simulated 325GHz channel data. For correction, the channels from the three option 325GHz and 183GHz are matched according to their weighting functions(Figure~\ref{fig:3ch:prel}). From the five  183 GHz and 325 GHz combinations possible, the weighting functions for channel-34 and channel-42 have the best match, thus we use this combination for the development of the correction scheme.

A simple regression approach is implemented to estimate the clear-sky values from the measurements. From the simulation dataset, 40000 clear-sky and the corresponding all-sky simulations are selected to develop the correction scheme. Without the availability of actual data, an identical simulation dataset but with noise is used mimic the measurements. The noise for individual channels is calculated according to Equation~\ref{eq:noise}. Before deriving any relationship between the different variables, 50\% of the clear-sky simulations are removed from the dataset. This clear-sky removal is to remove any under-representation of cloudy simulations, as discussed in the Validation section. Further, the simulations from channel-34 with cloud impact (clear - allsky) greater than 25 K are considered as "too cloudy" and are not included in the correction.

Among the various possible combinations of clear-sky and all-sky pairs for channel-34 and channel-43, the brightness temperature (TB)  differences of channels-34 and 42 are found to be reasonably well correlated against the channel-34 cloud impact (TB clear-sky minus all-sky ). Figure ~\ref{fig:fit:c34-42}  shows the scatter plot of the TB channel-34 minus TB channel-42 against the channel-34 cloud impact. The regression between the two variables gives the correction estimate for channel-34 all-sky measurements :
\begin{equation}
correction = tb^{34} + f(tb0^{42}_{as} - tb0^{32}_{cs})   
\end{equation}
where, $ tb^{34}$ are channel-34 measurements, and $tb0^{42}_{as}$ and $tb0^{32}_{cs}$ are channel-42 and channel-34 simulations for all-sky and clear-sky respectively. 
The correction is applied only to cloudy measurements. If TB differences between the measurements from channel-34 and channel-42 are less than 0.2 K or are greater than 25 K, they are considered as ``clear'' or ``too cloudy''  respectively and are not corrected. Further, it is also important to not to correct the cases which are classified as cloudy, but are clear instead. To avoid correcting such cases, another check is introduced. Assuming cloud impact for clear-sky cases in channel-34 to be twice the standard deviation of noise, the corresponding TB difference between measurements from channel-34 and 42 is interpolated from the fit. This value is assumed to be an estimate of the ``clear-sky threshold''. All measurements with TB differences between channel-34 and 42 less than this threshold are assumed to be true cloudy cases and are corrected.

The error in the predicted measurements is assessed by calculating the deviation to noise-free clear-sky observations. The occurrence frequency of the deviations is shown in Figure~\ref{fig:correction:c34-42}. The value in parentheses in the legend is the average bias for each dataset. If all measurements are correctly adjusted for cloud impact, the deviations should follow the gaussian distribution of noise. However, without any correction, the distribution function is skewed towards the left, indicating the presence of clouds (orange line). This cloudy impact is slightly reduced when cases with cloud impact greater than 25 K  are removed (green line). The reduction is mostly for cases with low TBs, indicating ``too cloudy'' measurements. When the regression approach is applied to adjust the remaining cloudy cases, the cloud impact in the measurements is considerably reduced, though the spread increases (red line). The sensitivity of the algorithm to correctly adjust the cloudy cases two different values of the noise-index: $1 \sigma$ and $2\sigma$. As evident from the figure, both values give almost similar results indicating that the algorithm can correctly identify and adjust most of the cloudy measurements.
